Spatial Analysis

### 2021-11-29 Scripts/spatial_analisis.Rmd
Re ran analysis to include Wanchese, NC

# Load ports
ports_data <- read_excel(ports_path,sheet = 2) %>% 
  clean_names() %>%
  mutate_if(is.character,
            ~ str_to_lower(.)
  ) %>% 
  mutate(
    species_name = ifelse(str_detect(common_name,"black"),"black sea bass",
                 ifelse(str_detect(common_name,"summer"),"summer flounder",
                        common_name)
    ),
    total_live_pounds = as.numeric(total_live_pounds),
    total_value = as.numeric(total_value)
  ) %>% 
  filter(
    !port_name %in% c("**roll-up to state-wide**","**roll-up to coast-wide**","unknown")
  )
```

@@

top_ports <- bind_rows(
  # 75th percentile used in project
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.25,year_ton) %>%  # top 75
    mutate(tresh = "75th"),
  # -------------------- #
  # For sensitivity values
  # -------------------- #
  # 95%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.5,year_ton) %>%  
    mutate(tresh = "95th"),
  # 85%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.15,year_ton) %>% 
    mutate(tresh = "85th"),
  # 65%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.35,year_ton) %>%  # top 75
    mutate(tresh = "65th"),
  # 50%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.5,year_ton) %>%  # top 75
    mutate(tresh = "50th")
)

@@

# Save data for future analysis
# write_csv(noaa_ports_complete,
#           my_path("D","Partial", name = "top_ports.csv")
#           )

@@

@@

# Get the overlapping segments 
# NOTE: Takes some gooooood time (~20 min)
Sys.time()
grid_eez_sf_fp <- st_intersection(grid_fp_sf,eez_sf)
Sys.time()

write_sf(grid_eez_sf_fp, my_path("D", "Partial/grid_fp",name="grid_eez_fp.shp"))

# Get final df with index
grid_eez_fp_df <- as.data.frame(grid_eez_sf_fp) %>%
  select(index,port_name,abrev=state_postal,spp=species_name) %>% 
  left_join(ne_grid,
            by = "index")

@@

grids_sw <- bind_rows(
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Paralichthys dentatus"),
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Stenotomus chrysops"),
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Centropristis striata")
) %>% 
  mutate(spatial = "sw",
         port_name = NA,
         abrev = NA
         )

>>>>

# Load ports
ports_data <- read_excel(ports_path,sheet = 2) %>% 
  clean_names() %>%
  mutate_if(is.character,
            ~ str_to_lower(.)
  ) %>% 
  mutate(
    species_name = ifelse(str_detect(common_name,"black"),"black sea bass",
                 ifelse(str_detect(common_name,"summer"),"summer flounder",
                        common_name)
    ),
    total_live_pounds = as.numeric(total_live_pounds),
    total_value = as.numeric(total_value),
    # Allocate all bsb NC data to Wanchese
    port_name = ifelse(species_name == "black sea bass" & state_postal == "nc" & port_name == "unknown","wanchese",port_name)
  ) %>% 
  filter(
    !port_name %in% c("**roll-up to state-wide**","**roll-up to coast-wide**","unknown")
  )
```

@@

# quantiles_df <- overall_port_data %>% 
#   group_by(species_name) %>% 
#   summarise(
#     "95th" = quantile(year_ton, 0.95),
#     "75th" = quantile(year_ton, 0.75),
#     "50th" = quantile(year_ton, 0.50)) %>% 
#   gather("tresh","quant",`95th`:`50th`)
# 
# 
# top_portsb <- overall_port_data %>% 
#   left_join(quantiles_df,
#             by = "species_name") %>% 
#   mutate(
#     treshold = ifelse(year_ton >= quant,tresh,NA) 
#   )

top_ports <- bind_rows(
  # 75th percentile used in project
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.25,year_ton) %>%  # top 75
    mutate(tresh = "75th"),
  # -------------------- #
  # For sensitivity values
  # -------------------- #
  # 95%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.05,year_ton) %>%  
    mutate(tresh = "95th"), # top 95
  # 85%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.15,year_ton) %>% 
    mutate(tresh = "85th"), # top 85
  # 65%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.35,year_ton) %>%  # top 75
    mutate(tresh = "65th"),
  # 50%
  overall_port_data %>% 
    group_by(species_name) %>% 
    top_frac(0.5,year_ton) %>%  # top 50
    mutate(tresh = "50th")
)

@@

# Save data for future analysis
write_csv(noaa_ports_complete,
          my_path("D","Partial", name = "top_ports.csv")
          )

@@

# xmin      ymin      xmax      ymax 
# -82.57346  29.77459 -62.88543  49.19141

@@

# Get the overlapping segments 
# NOTE: Takes some gooooood time (~ min)
Sys.time()
grid_eez_sf_fp <- st_intersection(grid_fp_sf,eez_sf)
Sys.time()

grid_eez_sf_fp_save <- grid_eez_sf_fp %>% 
  select(spp = species_name,
         index,
         port_name,
         abrev = state_postal,
         geometry) %>% 
  left_join(as.data.frame(land_sf),
            by = "abrev") %>% 
  select(-geom,-ID)

write_sf(grid_eez_sf_fp_save, my_path("D", "Partial/grid_fp",name="grid_eez_fp.shp"))

# Get final df with index
grid_eez_fp_df <- as.data.frame(st_coordinates(grid_eez_sf_fp_save)) %>% 
  rename(lon = X, lat = Y) %>% 
  bind_cols(grid_eez_sf_fp_save) %>% 
  select(-geometry)

@@

grids_sw <- bind_rows(
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Paralichthys dentatus"),
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Stenotomus chrysops"),
  my_path("D", "Partial/grid_sw", name = "grid_eez_sw_df.csv", read = T) %>% 
    mutate(spp = "Centropristis striata")
) %>% 
  left_join(land_sf) %>% 
  select(index,state,abrev,lat,lon,spp) %>% 
  mutate(spatial = "sw",
         port_name = NA
         )
